Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-25 rates-neurips-21/rates.tex
rate refs

@@

>>>>

\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

@@

Some references; will move:
\begin{itemize}
\item Binary classification.
  \begin{itemize}
  \item \citet{zhang2004statistical} -- early analysis, didn't use ``surrogate'' but had some quantitative bounds that implied consistency
  \item \citet{bartlett2006convexity} -- some bounds for margin losses
  \item \citet{reid2009surrogate} -- tight (?) bounds for general proper composite losses
  \end{itemize}

\item Weighted / cost-sensitive variants
  \begin{itemize}
  \item \citet{scott2011surrogate} -- weird example-dependent problem
  \item \citet{scott2012calibrated} -- general cost-sensitive binary classification
  \end{itemize}

\item Bipartite ranking (which is basically a set of pairwise binary classifications)
  \begin{itemize}
  \item \citet{agarwal2014surrogate} -- builds on binary classification losses (Mark + Bob), introduces strongly proper
  \item \citet{menon2016bipartite} -- different sort of regret bound, same problem
  \end{itemize}

\item Polyhedral regret bounds
  \begin{itemize}
  \item \citet{ramaswamy2018consistent} -- Abstain paper; shows bounds for 3 different surrogates, all linear, each ``from scratch''.  (Should we see what bounds we get??)
  \item 
  \end{itemize}

\item Fast rates for exp-concave surrogates ($O(d/n)$ where $d$ is the dimension) \citep{koren2015fast}.  Note here exp-concavex is in the \emph{parameter}.  So $F(\theta) = L(h_\theta(x),y)$ should be exp-concave in $\theta$.  For $\alpha>0$ we say $f$ is $\alpha$-exp-concave if $x \mapsto \exp(-\alpha f(x))$ is concave.
\end{itemize}
